The Application of Magnetic Susceptibility Separation for Measuring Cerebral Oxygenation in Preterm Neonates

### 2024-06-25 _tex/index.tex
Built site for gh-pages

\raggedbottom
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

@@

\begin{table}

@@

    \begin{tabular*}{\textwidth}{@{}p{2.5cm}llp{2.5cm}p{2.5cm}@{}}
    \toprule
        ~ & T1w & T2w & pcASL & SWI \\ \midrule
        Sequence & 3D FSPGR & 3D CUBE & Multi-shot 3D fast spin-echo & 3D spoiled GRE flow-compensated \\
        Phase-encoding direction & Coronal & Sagittal & Axial & Axial \\
        TR (ms) & 7.74 & 2,300 & 4,680 & 30.9 \\
        TE (ms) & 2.97 & 66.29 & 10.55 & 5.24 \\
        Flip angle & 12$^{\circ}$ & 90$^{\circ}$ & 111$^{\circ}$ & 20$^{\circ}$ \\
        FOV (cm) & 20 & 20 & 24 & 25 \\
        Acquisition matrix & 512 x 512 & 256 x 256 & 128 x 128 & 256 x 256 \\
        In-plane resolution (mm) & 0.39 x 0.39 & 0.78 x 0.78 & 1.875 x 1.875 & 0.977 x 0.977 \\
        Slice thickness (mm) & 1 & 1 & 4 & 2, reconstructed to 1 with zero filling (ZIP2) \\
        Number of slices & 126 & 106 & 50 & 92 \\
        Additional parameters & n/a & n/a & 1,450 ms label period; 2,025 ms pulse label; 24 control-label pairs & n/a \\
        Scan duration & 4 min 39 s & 5 min 1 s & 5 min 26 s & 5 min 29 s \\ \botrule
    \end{tabular*}
    \footnotetext{T1w = T1-weighted; T2w = T2-weighted; pcASL = pseudo-continuous arterial spin labelling; SWI = susceptibility weighted imaging; FSPG = fast spoiled gradient echo; CUBE = General Electric name of sequence, not an acronym; GRE = gradient echo; ZIP2 = through-plane zero filling interpolation}

\end{table}%

@@

\begin{table}

@@

\begin{tabular}{@{}ll@{}}
    \toprule
Variable & Subject Data (n=19) \\
  \midrule
Gestational age, weeks (mean $\pm$ SD)                       & 28.8 $\pm$ 1.68                                                     \\
Corrected gestational age on scan day, weeks (mean $\pm$ SD) & 40.36 $\pm$ 1.4                                 \\
Number of male neonates (%)                                  & 10 (52.63)                          \\
Birth weight, g (mean $\pm$ SD)                              & 1276.05 $\pm$ 294.87                                                     \\
Weight on scan day, g (mean $\pm$ SD)                        & 3396.58 $\pm$ 597.72 \\
Days spent in NICU (median, IQR)                             & 53, 23                                               \\
Days on ventilation (median, IQR)                            & 31, 28.5                                 \\
\botrule
\end{tabular}
\footnotetext{SD = standard deviation; IQR = inter quartile range}

\end{table}%

@@

\begin{table}

\caption{\label{tbl-chistats}Summary of acquired physiological
parameters. Mean ± SD is shown for chi and SvO\textsubscript{2} values.
The P-value and 95\% confidence interval (CI) were obtained through the
comparison of values between QSM and paramagnetic maps; (n=19).}

    \begin{tabular}{@{}lllp{2cm}ll@{}}
    \toprule
        Region & Measure & QSM & Paramagnetic map & p-value & 95\% CI \\ \midrule
        \multirow{ 2}{*}{SSS} & Chi (ppm)     & 0.1 \pm 0.02                     & 0.21 \pm 0.05                     & \ensuremath{2.84\times 10^{-11}}                        & -0.13, -0.09           \\
                              & SvO$_{2}$(\%) & 72.46 \pm 3.43 & 58.14 \pm 7.3 & \ensuremath{6.12\times 10^{-10}} & 11.78, 16.85 \\
        \multirow{ 2}{*}{CCV} & Chi (ppm)     & 0.13 \pm 0.02             & 0.22 \pm 0.05             & \ensuremath{6.25\times 10^{-9}}                        & -0.1, -0.07           \\
                              & SvO$_{2}$(\%) & 68.71 \pm 3.46 & 57.69 \pm 6.97 & \ensuremath{2.16\times 10^{-9}} & 8.9, 13.13 \\
        \botrule
    \end{tabular}
    \footnotetext{QSM = quantitative susceptibility mapping; CI = confidence interval; SSS = superior sagitall sinus; CCV = central cerebral vein}

\end{table}%

>>>>

\raggedbottom
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

@@

\begingroup\fontsize{8}{10}\selectfont

\begin{ThreePartTable}
\begin{TableNotes}[para]
\item T1w = T1-weighted; T2w = T2-weighted; pcASL = pseudo-continuous arterial spin labelling; SWI = susceptibility weighted imaging; FSPG = fast spoiled gradient echo; CUBE = General Electric name of sequence, not an acronym; GRE = gradient echo; ZIP2 = through-plane zero filling interpolation
\end{TableNotes}

\begin{longtable}[t]{>{\raggedright\arraybackslash}p{8em}ll>{\raggedright\arraybackslash}p{9em}>{\raggedright\arraybackslash}p{9em}}

@@

\tabularnewline

\toprule
 & T1w & T2w & pcASL & SWI\\
\midrule
Sequence & 3D FSPGR & 3D CUBE & Multi-shot 3D fast spin-echo & 3D spoiled GRE flow-compensated\\
Phase-encoding direction & Coronal & Sagittal & Axial & Axial\\
TR (ms) & 7.74 & 2,300 & 4,680 & 30.9\\
TE (ms) & 2.97 & 66.29 & 10.55 & 5.24\\
Flip angle & 12° & 90° & 111° & 20°\\
FOV (cm) & 20 & 20 & 24 & 25\\
Acquisition matrix & 512 x 512 & 256 x 256 & 128 x 128 & 256 x 256\\
In-plane resolution (mm) & 0.39 x 0.39 & 0.78 x 0.78 & 1.875 x 1.875 & 0.977 x 0.977\\
Slice thickness (mm) & 1 & 1 & 4 & 2, reconstructed to 1 with zero filling (ZIP2)\\
Number of slices & 126 & 106 & 50 & 92\\
Additional parameters & n/a & n/a & 1,450 ms label period;\newline  2,025 ms pulse label;\newline  24 control-label pairs & n/a\\
Scan duration & 4 min 39 s & 5 min 1 s & 5 min 26 s & 5 min 29 s\\
\bottomrule
\insertTableNotes

\end{longtable}

\end{ThreePartTable}
\endgroup{}

@@

\begingroup\fontsize{9}{11}\selectfont

\begin{ThreePartTable}
\begin{TableNotes}[para]
\item SD = standard deviation; IQR = inter quartile range
\end{TableNotes}

\begin{longtable}[t]{lc}

@@

\tabularnewline

\toprule
Variable & Subject data (n = 19)\\
\midrule
Gestational age, weeks (mean ± SD) & 28.8 ± 1.68\\
Corrected gestational age on scan day, weeks (mean ± SD) & 40.36 ± 1.4\\
Number of male neonates (\%) & 10 (52.63)\\
Birth weight, g (mean ± SD) & 1276.05 ± 294.87\\
Weight on scan day, g (mean ± SD) & 3396.58 ± 597.72\\
Days spent in NICU (median, IQR) & 53, 23\\
Days on ventilation (median, IQR) & 31, 28.5\\
\bottomrule
\insertTableNotes

\end{longtable}

\end{ThreePartTable}
\endgroup{}

@@

\begingroup\fontsize{9}{11}\selectfont

\begin{ThreePartTable}
\begin{TableNotes}[para]
\item QSM = quantitative susceptibility mapping; CI = confidence interval; SSS = superior sagitall sinus; CCV = central cerebral vein
\end{TableNotes}

\begin{longtable}[t]{llcccc}

\caption{\label{tbl-chistats}Summary of acquired physiological
parameters. Mean \(\pm\) SD is shown for chi and SvO\textsubscript{2}
values. The P-value and 95\% confidence interval (CI) were obtained
through the comparison of values between QSM and paramagnetic maps;
(n=19).}

\tabularnewline

\toprule
Region & Measure & QSM & Paramagnetic map & p-value & 95\% CI\\
\midrule
SSS & Chi (ppm) & 0.1 ± 0.02 & 0.21 ± 0.05 & 2.84e-11 & -0.13, -0.09\\
SSS & SvO₂ (\%) & 72.46 ± 3.43 & 58.14 ± 7.3 & 6.12e-10 & 0.12, 0.17\\
CCV & Chi (ppm) & 0.13 ± 0.02 & 0.22 ± 0.05 & 6.25e-09 & -0.1, -0.07\\
CCV & SvO₂ (\%) & 68.71 ± 3.46 & 57.69 ± 6.97 & 2.16e-09 & 0.09, 0.13\\
\bottomrule
\insertTableNotes

\end{longtable}

\end{ThreePartTable}
\endgroup{}
